---
title: "Pitch"
author: "Lorenz Hexemer"
date: "2022-09-13"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Usecase

* You got tested for a virus infection by a quick test multiple times

* Due to uncertainty in the tests, the result sometimes shows a positive and sometimes a negative result

* Find out which scenario (infected or not) is more likely, given a series of results.

## Manual

* Select the sensitivity and specificity of the quick test.

* Select the result of the test (positive or negative)

* If you used different test, tune sensitivity and specificity

* The app calculates the probability of the given series of events under the two assumptions (infected or not)


## The math behind the app

In the infected scenario, the probability of a series depends on the sensitivity: The Probability of  
the first and the third test beeing positive and the second beeing negative if you are in fact infected is:

```{r echo=TRUE, message=TRUE}
  sensi <- 0.73
  p_infected <- prod(c(sensi, 1-sensi,sensi))
  p_infected
```

In the healthy scenario, the probability of a series depends on the specificity: The probability of  
the same series of results if you are in fact health is:

```{r echo=TRUE, message=TRUE}
  specificity <- 0.93
  p_healthy <- prod(c(1 - specificity,specificity,1-specificity))
  p_healthy
```
## A shiny app
The probabilities of the results are also visualized to help you interpreting the results.
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(png)
myimg <- readPNG("shiny_app.png")
plot.new()
rasterImage(myimg,0,0,1,1)
```


